Distributions

### 2022-01-05 Ch2_distributions/Ch2_Figures.Rmd
Editing first figure to show variation in both individuals and social groups.

```{r Figure1, fig.width=6, fig.height=4}

ptpl %>%
  ggplot(., aes((x = mpm))) +
  #geom_line(aes(x = mpm, group = id, color = fam_g), stat = "density", alpha = 0.8) +
  geom_line(aes(x = mpm, group = id), color = "grey", 
            stat = "density", alpha = 0.8) +
  # geom_line(aes(x = mpm, group = fam_g), stat = "density", alpha = 0.4,
  #           color = "blue") +
  geom_line(stat = "density", color = "black", lwd = 1) +
  geom_vline(xintercept = 0, color = "grey") +
  geom_hline(yintercept = 0, color = "grey") +
  labs(y = "Density", x = "Velocity in m/min") +
  theme_classic() +
  scale_color_manual(values = my.cols2) +
  theme(legend.position = "none")

>>>>

```{r Figure1, fig.width=12, fig.height=4}

zoom_dims <- c(90, 200, 0, 0.01)
annot_xy <- c(50, 200, 0.025, 0.045)
box_color <- "blue"

ind_dens_plot <- ptpl %>%
  ggplot(., aes((x = mpm))) +
  #geom_line(aes(x = mpm, group = id, color = fam_g), stat = "density", alpha = 0.8) +
  geom_line(aes(x = mpm, group = id), color = "grey", 
            stat = "density", alpha = 0.8) +
  geom_line(stat = "density", color = "black", lwd = 1) +
  geom_vline(xintercept = 0, color = "grey") +
  geom_hline(yintercept = 0, color = "grey") +
  labs(y = "Density", x = "Velocity in m/min") +
  # geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[2], y = zoom_dims[3], yend = zoom_dims[3]), color = box_color) +
  # geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[2], y = zoom_dims[4], yend = zoom_dims[4]), color = box_color) +
  # geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[1], y = zoom_dims[3], yend = zoom_dims[4]), color = box_color) +
  # geom_segment(aes(x = zoom_dims[2], xend = zoom_dims[2], y = zoom_dims[3], yend = zoom_dims[4]), color = box_color) +
  theme_classic() +
  scale_color_manual(values = my.cols2) +
  theme(legend.position = "none")

ind_dens_plot +
  coord_cartesian(
    xlim = zoom_dims[1:2],
    ylim = zoom_dims[3:4]) +
  theme(title = element_blank()) -> ind_zoom

ind_dens_plot +
  annotation_custom(grob = ggplotGrob(ind_zoom), xmin = annot_xy[1] , xmax = annot_xy[2] , ymin = annot_xy[3] , ymax = annot_xy[4]) -> a

fam_dens_plot <- ptpl %>%
  ggplot(., aes((x = mpm))) +
  #geom_line(aes(x = mpm, group = id, color = fam_g), stat = "density", alpha = 0.8) +
  geom_line(aes(x = mpm, group = fam_g), color = "grey", 
            stat = "density", alpha = 0.8) +
  geom_line(stat = "density", color = "black", lwd = 1) +
  geom_vline(xintercept = 0, color = "grey") +
  geom_hline(yintercept = 0, color = "grey") +
  labs(y = "Density", x = "Velocity in m/min") +
    # geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[2], y = zoom_dims[3], yend = zoom_dims[3]), color = box_color) +
  # geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[2], y = zoom_dims[4], yend = zoom_dims[4]), color = box_color) +
  # geom_segment(aes(x = zoom_dims[1], xend = zoom_dims[1], y = zoom_dims[3], yend = zoom_dims[4]), color = box_color) +
  # geom_segment(aes(x = zoom_dims[2], xend = zoom_dims[2], y = zoom_dims[3], yend = zoom_dims[4]), color = box_color) +
  theme_classic() +
  scale_color_manual(values = my.cols2) +
  theme(legend.position = "none")

fam_dens_plot +
  coord_cartesian(
    xlim = zoom_dims[1:2],
    ylim = zoom_dims[3:4]) +
  theme(title = element_blank()) -> fam_zoom

fam_dens_plot +
  annotation_custom(grob = ggplotGrob(fam_zoom), xmin = annot_xy[1] , xmax = annot_xy[2] , ymin = annot_xy[3] , ymax = annot_xy[4]) -> b

plot_grid(a, b)
